A Systematic Literature Review on Extensions to Role-Based Access Control

### 2014-02-08 paper/sections/categorization.tex
Removing duplicate paper and updating total counts.
Adding latest PDF and PNGs of images to be able to build with Latek.
Adding edits to various sections.
updates - 1. Reorganization results section 2. update Figure 2

\subsection{Definitions}

@@

  \item \textbf{Privacy (Priv)}: The RBAC extension model provides entities and mechanisms to describe privacy policies, which are legal statements or documents about disclosure or management of personally identifiable information such as name, address, or data of birth.

@@

\begin{figure}[ht]
    \centering
        \includegraphics[width=6.0in]{sections/category_structrure.eps}
\vspace{-0.7 in}
    \caption{\label{fig:category_structrure}Structure of categories within the RBAC extension models.}
\end{figure}

@@

The 28 primary sources produced a set of eight hierarchical categories. Table \ref{tab:categorization} summarizes each primary source under their designated category and furthermore, displays the perceived hierarchy of the categories. Figure~\ref{fig:category_structrure} shows the hierarchy structure among categories. The Constraint, Organizational, Privacy, Task, and Spatial and Temporal categories can be special cases of the Context category. The Spatio-Temporal category subsumes Spatial and Temporal categories. The Spatial and Temporal categories were treated as subsets of the broader category of Spatio-Temporal since this category encompasses them individually and the Spatio-Temporal category contained more primary sources that the Spatial or Temporal categories alone.

>>>>

@@

  \item \textbf{Privacy (Priv)}: The RBAC extension model provides entities and mechanisms to describe privacy policies, which are legal statements or documents about disclosure or management of personally identifiable information such as name, address, or date of birth.

@@

\begin{figure}[ht]
    \centering
        \includegraphics[width=6.0in]{sections/category_structrure.png}
%\vspace{-0.2 in}
    \caption{\label{fig:category_structrure}Structure of categories within the RBAC extension models.}
\end{figure}

@@

The 27 primary sources produced a set of eight hierarchical categories. Table \ref{tab:categorization} summarizes each primary source under their designated category and furthermore, displays the perceived hierarchy of the categories. Figure~\ref{fig:category_structrure} shows the hierarchy structure among categories. The Constraint, Organizational, Privacy, Task, and Spatial and Temporal categories can be special cases of the Context category. The Spatio-Temporal category subsumes Spatial and Temporal categories. The Spatial and Temporal categories were treated as subsets of the broader category of Spatio-Temporal since this category encompasses them individually and the Spatio-Temporal category contained more primary sources that the Spatial or Temporal categories alone.
